Tutorial for Runing Mouse Bone Marrow Dataset

### 2023-10-13 Demo_marrow_facs.Rmd
adjacency_mtx

# Running LMD Step by Step
This provides a step-by-step tutorial for a better understanding of the algorithm. If you want to generate results directly, please skip to 'Running LMD in One Step'
```{r}
source("./LMD_function.R", echo = F)
```
## Step1: Build KNN Graph
```{r}
# Construct knn graph
W = Symmetric_KNN_graph(knn = 5, feature_space = feature_space)[[1]]

>>>>

# Running LMD Step by Step
This provides a step-by-step tutorial for a better understanding of the algorithm. If you want to generate results directly, please skip to 'Running LMD in One Step'
```{r}
source("./LMD_function.R", echo = F)
```
## Step1: Build KNN Graph
```{r}
# Construct knn graph
res = Symmetric_KNN_graph(knn = 5, feature_space = feature_space)

A = res$adj_matrix # Adjacency Matrix
W = res$graph # Symmetrized Graph ((A + AT) / 2)
